Genetic draft and the evolution of ``irreducible complexity"

### 2023-02-27 manuscript/response_to_reviews.tex

\begin{document}

\section*{Associate Editor}

\begin{reviewerquote}
As mentioned by all referees, the non-standard setup of the simulation scheme makes it very difficult to relate the results to previous work. Although your main conclusion may well be confirmed for a standard infinite-sites model without constraining the background variance, this is by no means guaranteed (see the remarks about the infinitesimal limit by referee 2). To address this point (in the absence of analytical results), there is probably no way around individual-based simulations.
\end{reviewerquote}

We have redone most of the simulations in this paper using \texttt{WaveFit}, a custom simulation package written in Julia for running individually-based simulations using an infinite sites model for the background fitness linked to two focal loci. Though the original \texttt{FFPopSim} simulations were individual-based, we have replaced our results completely with results from \texttt{WaveFit}.
%though groups of individuals identical in fitness are abstracted away as "clones" during the natural selection step. We have made this clearer.

@@

We have fixed this.

\begin{reviewerquote}
3. page 7, first paragraph of Results: Why is the null expectation that genetic draft increases the time for valley crossing? At least in their abstract, Neher \& Shraiman (2011) appear to claim the opposite trend (last sentence). Or is this only true in the presence of recombination?
\end{reviewerquote}

We agree that the null expectation is not really clear in this case. We have amended the text accordingly.

Neher and Shraiman (2011) determined that the opposite trend applies in the case where $1/N < \delta \lesssim sigma$. In this case, the stochastic effects of genetic draft can propel a deleterious mutation to high frequencies, allowing valley crossing to occur more quickly. The bubble size distribution, which determines the number of opportunities there are for a successful complex adaptation to appear and establish, drops off more quickly in the case of draft ($1/n^2$) than drift ($1/n$). So the overall rate of crossing should be higher in the draft case \emph{for neutral intermediates, or intermediates of small effect}. When the effect is large, the drift bubble size distribution is harshly cut off around $1/\delta^2$. The draft bubble size distribution is not. So the crossing rate is \emph{lower} in the case of neutral or weak intermediates. In addition, in a drafting population, clonal interference/multiple mutation effects retard the growth and fixation of the complex adaptation once it appears. So that, too, slows down the crossing rate in the draft case.
